---
title: "Cabbages"
author: "Natasha Lekach"
date: "February 13, 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicCN <- ggplot(veggy,aes(x=Cult,y=VitC))
```
## Now add in boxplot
Vitamin C Content by Cultivation Factor  
```{r}
basicCN + geom_boxplot()
```
  
These boxplots show that the c39 cultivation method has, on average, less Vitamin C than the c52 cultivation method. The median vitamin c content for the c39 cultivation method is about 52 and just under 65 for c52.  

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```
  
This table shows that, on average, the c39 cultivation method has less vitamin c than the c52 cultivation method. For example, the average vitamin c content is 51.5 for c39 and 64.4 for c52.
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```
  
The p-value for this t-test is 0.00000003495. There is a 0.000003495% chance that the null hypothesis is correct. Therefore, we reject the null hypothesis and accept the alternative hypothesis. The alternative hypothesis states that there is a statistically significant difference between the average vitamin c content in the two cultivation methods.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
